---
title: "Building Energy Performance Analysis"
author: "Adam Dennett"
date: "2024-02-22"
output: html_document
---

## Downloading EPC Data using the API

The code below (translated into R from the python examples given here: <https://epc.opendatacommunities.org/docs/api/domestic>) will download all of the data for a particular local authority of interest:

```{r}
library(httr)
library(here)
library(janitor)

source("keys.r")

# Page size (max 5000)
query_size <- 5000
# Output file name
#output_file <- 'output.csv'
output_file <- here("content", "teaching", "2024-02-20-EPC_Data", "data", "output.csv")

# Base url and example query parameters
base_url <- 'https://epc.opendatacommunities.org/api/v1/domestic/search'

#this parameter specifies a particular local authority
query_params <- list(size = query_size, `local-authority` = 'E07000228')

# Set up authentication
headers <- c(
  'Accept' = 'text/csv',
  'Authorization' = epc_auth
)

# Keep track of whether we have made at least one request for CSV headers and search-after
first_request <- TRUE
# Keep track of search-after from previous request
search_after <- NULL

# Open a connection to write to the output file
file_conn <- file(output_file, "w")

# Loop over entries in query blocks of up to 5000 to write all the data into a file
while (!is.null(search_after) || first_request) {
  # Only set search-after if this isn't the first request
  if (!first_request) {
    query_params[["search-after"]] <- search_after
  }
  
  # Make request
  response <- GET(url = base_url, query = query_params, add_headers(.headers=headers))
  response_body <- content(response, as = "text")
  search_after <- headers(response)$`X-Next-Search-After`
  
  # For CSV data, only keep the header row from the first response
  if (!first_request && response_body != "") {
    response_body <- strsplit(response_body, "\n")[[1]][-1]
  }
  
  # Write received data
  writeLines(response_body, file_conn)
  
  first_request <- FALSE
}

# Close the file connection
close(file_conn)
```

Read the CSV file back in to your environment

```{r}
library(tidyverse)

epc_data <- read_csv(here("content", "teaching", "2024-02-20-EPC_Data", "data", "output.csv")) %>% 
  clean_names()
```

## Get UPRN Data from the OS API

The osdatahub package makes this much easier to achieve.

```{r}
library(osdatahub)
library(zip)

#API key - although this isn't needed for the open data
key <- os_auth

#get a list of the open datasets
list_os_opendata()

#we're interested in the OpenUPRN dataset, so get all of the relevant info into an object
uprn = list_os_opendata('OpenUPRN')

#opening up the object, can see that we want the csv, which is the first entry
uprn$fileName[1]

#now we can download it:
download_os_opendata(uprn, 
                     file_name = uprn$fileName[1], 
                     output_dir = tempdir())

#get the path to the zipfile you have just downloaded
zip_file <- file.path(tempdir(), uprn$fileName[1])
#find out what the name of the csv is within the zipfile
zip_contents <- zip_list(zip_file)
zip_contents$filename[3]
csv_file <- zip_contents$filename[3]

# Unzip the file
unzip(zipfile = zip_file, exdir = tempdir())

# Read data from the CSV file
uprn_data <- read_csv(file.path(tempdir(), csv_file)) %>% 
  clean_names()

```

Get some Local Authority Boundaries

```{r}
library(geojsonsf)
library(tmap)

LAD_sf <- geojson_sf("https://services1.arcgis.com/ESMARspQHYMw9BZ9/arcgis/rest/services/Local_Authority_Districts_December_2023_Boundaries_UK_BFC/FeatureServer/0/query?outFields=*&where=1%3D1&f=geojson") 

qtm(LAD_sf)

Local_sf <- LAD_sf %>% filter(LAD23CD == "E07000228")

qtm(Local_sf)
```

Now we can join some coordinates to our EPC data to enable some mapping

```{r}
str(epc_data)
str(uprn_data)

#filter out all of the rows without uprns (and therefore coordinates)
epc_coords <- left_join(epc_data, uprn_data, by = join_by(uprn == uprn)) %>% 
  filter(!is.na(uprn))

write_csv(epc_coords, here("content", "teaching", "2024-02-20-EPC_Data", "data", "epc_coords.csv"))
```

Now we can map it!

```{r}
library(sf)

epc_sf <- st_as_sf(epc_coords, coords=c("x_coordinate", "y_coordinate"), crs=27700)

st_crs(Local_sf)
Local_sf <- st_transform(Local_sf, 27700)

#clip it as some weird places
epc_sf_clip <- epc_sf[Local_sf,]


```

```{r}
library(tmap)

tmap_mode("plot")
qtm(epc_sf_clip)
```
